A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-01-30 paper.tex
removing 10draft

%\begin{prop}
%Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$. Denote by $\phi, \phi^*$ sections of $E_1,E_1^![-1]$ and by $\psi, \psi^*$ sections of $E_1^!, E_1[-1]$. Suppose
%\[Q_{\mr{BV}}\phi + \{I, \phi\} = \phi - f_\psi \in E_1[-1] ,\qquad Q\psi + \{I, \psi\} = \psi - f_{\phi} \in E_1^![-1],\]
%where $f_\phi$ is independent of $\psi$ and $f_{\psi}$ is independent of $\phi$. Then the theory $(E, Q_{\mr{BV}}, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action obtained by setting $\phi = f_\psi, \phi^* = 0,  \psi = f_\phi, \psi^* = 0$ in the original BV action.
%\label{prop:BRSTdoublet}
%\end{prop}

@@

\begin{theorem}
The holomorphic twist of 10d $\mc N=(1, 0)$ super Yang--Mills on $M=\RR^{10}$ is perturbatively equivalent to the holomorphic Chern--Simons theory on $M\cong\CC^5$ with the space of fields $\map(M, B\gg)$. Moreover, the equivalence is $\SU(5)$-equivariant.
\label{thm:10dholomorphictwist}
\end{theorem}
\begin{proof}
First, we may eliminate $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}. So, the above theory is perturbatively equivalent to the theory without $\chi$ and $\chi^*$ with the BV action
\begin{align*}
S_{\text{no }\chi} &= \int \dvol \left(-(F_{2, 0}, F_{0, 2}) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
&+ \int \dvol\left((\dd_{A_{1, 0}} c, A_{1, 0}^*) + (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([\rho, c], \rho^*) + ([B, c], B^*) + \frac{1}{2}[c, c]c^*\right) \\
&+ \int \dvol(-(\psi, A_{1, 0}^*) + (F_{0, 2}, B^*))
\end{align*}

@@

We use the same twisting homomorphism $\phi : \MU(2) \to \Spin(6;\CC)$ and twisting data $\alpha : U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
Then, $S_+ \otimes W$ decomposes nuder $\MU(2)$ as
\[
S_+\otimes W\cong L\oplus L^*\oplus \det(L)\oplus \CC \cdot Q_0 \oplus \CC \cdot \Bar{Q}_0 \oplus \det(L)^{-1}.
\]

@@

\subsubsection{Minimal Twist}
\label{sect:3d8minimal_twist}
The 3d $\cN=8$ super Yang--Mills viewed as an $\cN=4$ supersymmetric theory coincides with the 3d $\cN=4$ super Yang--Mills with matter valued in the representation $U = T^*\gg$. From Theorem \ref{3d_4_minimal_twist_thm} we obtain the following statement.

>>>>

\begin{prop}
Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus E_1\oplus E_1^![-1]\oplus E_1^!\oplus E_1[-1]$. Denote by $\phi, \phi^*$ sections of $E_1,E_1^![-1]$ and by $\psi, \psi^*$ sections of $E_1^!, E_1[-1]$. Suppose
\[Q_{\mr{BV}}\phi + \{I, \phi\} = \phi - f_\psi \in E_1[-1] ,\qquad Q\psi + \{I, \psi\} = \psi - f_{\phi} \in E_1^![-1],\]
where $f_\phi$ is independent of $\psi$ and $f_{\psi}$ is independent of $\phi$. Then the theory $(E, Q_{\mr{BV}}, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action obtained by setting $\phi = f_\psi, \phi^* = 0,  \psi = f_\phi, \psi^* = 0$ in the original BV action.
%\label{prop:BRSTdoublet}
\end{prop}

@@

\begin{theorem}
The holomorphic twist of 10d $\mc N=(1, 0)$ super Yang--Mills on $M=\RR^{10}$ is perturbatively equivalent to the holomorphic Chern--Simons theory on $M\cong\CC^5$ with the space of fields $\map(M, B\gg)$. Moreover, the equivalence is $\SU(5)$-equivariant.
\label{thm:10dholomorphictwist}
\end{theorem}
\begin{proof}
First, we may eliminate $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}. So, the above theory is perturbatively equivalent to the theory without $\chi$ and $\chi^*$ with the BV action
\begin{align*}
S_{\text{no }\chi} &= \int \dvol \left(-(F_{2, 0}, F_{0, 2}) + (B, \dd_{A_{1, 0}} \rho)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
&+ \int \dvol\left((\dd_{A_{1, 0}} c, A_{1, 0}^*) + (\ol\dd_{A_{0, 1}} c, A_{0, 1}^*) + ([\rho, c], \rho^*) + ([B, c], B^*) + \frac{1}{2}[c, c]c^*\right) \\
&+ \int \dvol(-(\rho, A_{1, 0}^*) + (F_{0, 2}, B^*))
\end{align*}

@@

We use the same twisting homomorphism $\phi : \MU(2) \to \Spin(6;\CC)$ and twisting data $\alpha : U(1) \to G_R$ as in Section \ref{sect:4d4holomorphictwist}.
Then, $S_+ \otimes W$ decomposes under $\MU(2)$ as
\[
S_+\otimes W\cong L\oplus L^*\oplus \det(L)\oplus \CC \cdot Q_0 \oplus \CC \cdot \Bar{Q}_0 \oplus \det(L)^{-1}.
\]

@@

\subsubsection{Minimal Twist}
\label{sect:3d8minimal_twist}
The 3d $\cN=8$ super Yang--Mills viewed as an $\cN=4$ supersymmetric theory coincides with the 3d $\cN=4$ super Yang--Mills with matter valued in the representation $U = T^*\gg$.  Alternatively, it is obtained by dimensional reduction from the holomorphic twist of 4d $\mc N=4$ super Yang-Mills.  From Theorem \ref{3d_4_minimal_twist_thm} we obtain the following statement.
